### 2018-08-23 doc/large_strain.tex
summarize current formation=1 algorithm

@@

Neo-Hookean model
\begin{gather}
\psi \left( \mathbf{C} \right)
  = \frac{\mu}{2} \left[ \trace{\mathbf{C}} - \trace{\mathbf{I}} - 2 \ln\left( J \right) \right]
  - \lambda \ln^{2}\left( J \right)
\end{gather}
where $\mu$ and $\lambda$ respectively denote the shear modulus and Lam\'{e} parameter,
and the volumetric Jacobian $J = \det\left(\mathbf{F}\right) = \sqrt{\det\left(\mathbf{C}\right)}$.
\begin{gather}
\frac{d \psi \left( \mathbf{C} \right)}{d \mathbf{C}}
  = \frac{\mu}{2} \mathbf{I} - \frac{1}{2} \left[ \mu - 2\lambda\ln\left( J \right) \right] \mathbf{C}^{-1}
\end{gather}
\begin{gather}
\frac{d^{2} \psi \left( \mathbf{C} \right)}{d \mathbf{C} \otimes d \mathbf{C}}
  = \left[ \mu - 2\lambda\ln\left( J \right) \right] \left[ - \frac{d \mathbf{C}^{-1}}{d \mathbf{C}} \right]
  + \frac{\lambda}{2} \mathbf{C}^{-1} \otimes \mathbf{C}^{-1}
\end{gather}

Denoting $\chi\left( \bullet \right)$ as the Piola transformation, which implies
\begin{gather}
\chi\left( \mathbf{A} \right)_{ij}
  = F_{iA} A_{AB} F_{jB} \\
\chi\left( \boldsymbol{\mathcal{A}} \right)_{ijkl}
  = F_{iA} F_{jB} \mathcal{A}_{ABCD} F_{kC} F_{lD} 
\end{gather}
for rank-2 and rank-4 tensors $\mathbf{A}$ and $\boldsymbol{\mathcal{A}}$, then the Kirchhoff stress and its associated material tangent are
\begin{gather}
\boldsymbol{\tau}
  \equiv J \boldsymbol{\sigma}
  = \chi\left( 2 \frac{d \psi \left( \mathbf{C} \right)}{d \mathbf{C}} \right)
  = \mu \mathbf{b} - \left[ \mu - 2\lambda\ln\left( J \right) \right] \mathbf{I}
\end{gather}
and 
\begin{gather}
J \boldsymbol{\mathcal{C}}
  = \chi\left( 4 \frac{d^{2} \psi \left( \mathbf{C} \right)}{d \mathbf{C} \otimes d \mathbf{C}} \right)
  = \left[ \mu - 2\lambda\ln\left( J \right) \right] \boldsymbol{\mathcal{S}}
  + \frac{\lambda}{2} \mathbf{I} \otimes \mathbf{I}
\end{gather}
where $\boldsymbol{\mathcal{S}}$ is the fourth-order symmetric identity tensor.
The action that $J \boldsymbol{\mathcal{C}}$ performs when contracted with an arbitrary rank-2 symmetric tensor is therefore
\begin{gather}
J \boldsymbol{\mathcal{C}} : \left( \bullet \right)
  = \left[ \mu - 2\lambda\ln\left( J \right) \right] \left( \bullet \right)
  + \frac{\lambda}{2} \trace\left( \bullet \right) \mathbf{I}
\end{gather}

@@

>>>>

\usepackage[linesnumbered,lined,commentsnumbered,ruled]{algorithm2e}

@@

Neo-Hookean model
\begin{gather}
\psi \left( \mathbf{C} \right)
  = \frac{\mu}{2} \left[ \trace{\mathbf{C}} - \trace{\mathbf{I}} - 2 \ln\left( J \right) \right]
  + \lambda \ln^{2}\left( J \right)
\end{gather}
where $\mu$ and $\lambda$ respectively denote the shear modulus and Lam\'{e} parameter,
and the volumetric Jacobian $J = \det\left(\mathbf{F}\right) = \sqrt{\det\left(\mathbf{C}\right)}$.
\begin{gather}
\frac{d \psi \left( \mathbf{C} \right)}{d \mathbf{C}}
  = \frac{\mu}{2} \mathbf{I} - \frac{1}{2} \left[ \mu - 2\lambda\ln\left( J \right) \right] \mathbf{C}^{-1}
\end{gather}
\begin{gather}
\frac{d^{2} \psi \left( \mathbf{C} \right)}{d \mathbf{C} \otimes d \mathbf{C}}
  = \frac{1}{2}\left[ \mu - 2\lambda\ln\left( J \right) \right] \left[ - \frac{d \mathbf{C}^{-1}}{d \mathbf{C}} \right]
  + \frac{\lambda}{2} \mathbf{C}^{-1} \otimes \mathbf{C}^{-1}
\end{gather}

Denoting $\chi\left( \bullet \right)$ as the Piola transformation, which implies
\begin{gather}
\chi\left( \mathbf{A} \right)_{ij}
  = F_{iA} A_{AB} F_{jB} \\
\chi\left( \boldsymbol{\mathcal{A}} \right)_{ijkl}
  = F_{iA} F_{jB} \mathcal{A}_{ABCD} F_{kC} F_{lD}
\end{gather}
for rank-2 and rank-4 tensors $\mathbf{A}$ and $\boldsymbol{\mathcal{A}}$, then the Kirchhoff stress and its associated material tangent are
\begin{gather}
\boldsymbol{\tau}
  \equiv J \boldsymbol{\sigma}
  = \chi\left( 2 \frac{d \psi \left( \mathbf{C} \right)}{d \mathbf{C}} \right)
  = \mu \mathbf{b} - \left[ \mu - 2\lambda\ln\left( J \right) \right] \mathbf{I}
\end{gather}
and
\begin{gather}
J \boldsymbol{\mathcal{C}}
  = \chi\left( 4 \frac{d^{2} \psi \left( \mathbf{C} \right)}{d \mathbf{C} \otimes d \mathbf{C}} \right)
  = 2 \left[ \mu - 2\lambda\ln\left( J \right) \right] \boldsymbol{\mathcal{S}}
  + 2 \lambda \mathbf{I} \otimes \mathbf{I}
\end{gather}
where $\boldsymbol{\mathcal{S}}$ is the fourth-order symmetric identity tensor.
The action that $J \boldsymbol{\mathcal{C}}$ performs when contracted with an arbitrary rank-2 symmetric tensor is therefore
\begin{gather}
J \boldsymbol{\mathcal{C}} : \left( \bullet \right)
  = 2 \left[ \mu - 2\lambda\ln\left( J \right) \right] \left( \bullet \right)
  + 2 \lambda \trace\left( \bullet \right) \mathbf{I}
\end{gather}

@@

Due to the specifics of matrix-free operator evaluation in \texttt{deal.II}, when performing contraction with gradient of shape functions in current (deformed) configuration, the integration is also done over the deformed configuration. Therefore in order to arrive at the integral in undeformed configuration, additionally we have to divide by Jacobian $J$ of the mapping at a given quadrature point.

\begin{algorithm}[h]
  \SetKwInOut{Input}{Given}
  \SetKwInOut{Output}{Return}
  \Input{RHS FE vector $\gz x$, current FE solution $\gz u$,
  cacheed $c_1 := \mu - 2 \lambda \log(J)$ for each cell and quadrature point}
  \Output{action of the FE tangent on $\gz x$}
  \ForEach{ element $K \in \Omega^h$ }{
        \ForEach{quadrature point $q$ on $K$}{
          evaluate $\gz \nabla_X \gz u^h$ \tcp*{2nd order}
          evaluate $\gz F = \gz I + \gz \nabla_X \gz u^h$ \tcp*{2nd order}
          evaluate $J = \rm{det}(\gz F)$ \tcp*{scalar}
          evaluate $\gz b = \gz F \cdot \gz F^T$ \tcp*{2nd order symmetric}
          evaluate $\gz x_1 := \gz \nabla \gz x$ \tcp*{2nd order}
          evaluate $\gz \tau = \mu \gz b - c_1 \gz I$ \tcp*{2nd order symmetric}
          evaluate $J \boldsymbol{\mathcal{G}} = x_1 \cdot \gz \tau$ \tcp*{2nd order symmetric}
          ``submit'' contraction $\left[\gz \nabla \gz N_i : J\boldsymbol{\mathcal{G}}\right] / J$\;
          evaluate $\gz x_2 := \gz \nabla_{sym} \gz x$ \tcp*{2nd order symmetric}
          evaluate $J \boldsymbol{\mathcal{C}} = 2 c_1 \gz x_2 + 2 \lambda \rm{tr}( \gz x_2) \gz I $ \tcp*{2nd order symmetric}
          ``submit'' contraction $\left[\gz \nabla_{sym} \gz N_i : J \boldsymbol{\mathcal{C}} \right]/ J$ \;
        }
  }
  \caption{Matrix-free tangent cell operator, variant 1: minimum caching.}
  \label{alg:mf_multivector}
\end{algorithm}
